An Approach to Off-line Handwriting Recognition through Segmentation Techniques and Deep Neural Networks

### 2017-12-17 Report/paper.tex
a

\subsection{Line selection}
As the ordening of the words % TODO, verklaar waarom die ordening weggat? 
we place the words in lines, and orden these lines. 
Algorithm \ref{alg:linereconstr} shows the pseudocode of our line selection process.
The algorithm reorders the words in lines and orders these lines as ordered in the original text.

>>>>

\subsection{Line selection}
Because the contour finding algorithm has no particular order in which it saves the found contours, we have to reorder the found words in their original lines.
Algorithm \ref{alg:linereconstr} shows the pseudocode of our line selection process.
The algorithm reorders the words in lines and orders these lines as ordered in the original text.
